Paper

### 2018-11-13 paper.Rmd
more on sps diversity effects

f6$nodf.song<-out.site$nodf.song[match(f6$Site_ID, out.site$Site_id)]
f6$int_evenness<-out.site$int_evenness[match(f6$Site_ID, out.site$Site_id)]
f6$H2<-out.site$H2[match(f6$Site_ID, out.site$Site_id)]
f6$functional.comp.poll<-out.site$functional.comp.poll[match(f6$Site_ID, out.site$Site_id)]
f6$niche.overlap.plant<-out.site$niche.overlap.plant[match(f6$Site_ID, out.site$Site_id)]
f6$modularity<-out.site$modularity[match(f6$Site_ID, out.site$Site_id)]

@@

>>>>

f6$nodf.song<-out.site$nodf.song[match(f6$Site_ID, out.site$Site_id)]
f6$int_evenness<-out.site$int_evenness[match(f6$Site_ID, out.site$Site_id)]
f6$H2<-out.site$H2[match(f6$Site_ID, out.site$Site_id)]
f6$functional.comp.poll<-out.site$functional.comp.poll[match(f6$Site_ID, out.site$Site_id)]
f6$niche.overlap.plant<-out.site$niche.overlap.plant[match(f6$Site_ID, out.site$Site_id)]
f6$modularity<-out.site$modularity[match(f6$Site_ID, out.site$Site_id)]
f6$species.poll<-out.site$species.poll[match(f6$Site_ID, out.site$Site_id)]
f6$species.pl<-out.site$species.pl[match(f6$Site_ID, out.site$Site_id)]

@@

#also analyze effect of diversity

m.th.poll.div<-glmmTMB(no_rows ~ species.poll , family="gaussian", data=f6)
summary(m.th.poll.div)

m.th.pl.div<-glmmTMB(no_rows ~ species.pl , family="gaussian", data=f6)
summary(m.th.pl.div)

pl.th3<-ggplot(f6,  aes(x=species.pl, y=no_rows))+      
        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
        xlab("Plant species diversity") +      
        ylab("Evenness in fruitset") + theme_bw() + 
        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))

pl.th3
